---
title: "Pop_Analysis"
output: html_document
date: "2025-05-13"
---

###Library Set Up

```{r Library Setup}
#creating percentages and tidying data
library(dplyr)
#perform glmm
library(glmmTMB)
#perform analysis of deviance
library(car)
#check for multicolinearity
library(performance)
#perform a glm.nb
library(MASS)
#post-hoc contrasts in models 
library(emmeans)
#GGPlot Packages
library(ggplot2)
```

###Import and Clean Data 

```{r Import data set}
setwd("/Users/niamhmccartan/Documents/College/PhD/Papers/Population/Pop_R")

full <- read.csv("Pop_full.csv", header = TRUE, stringsAsFactors = FALSE)
```
```{r Remove any unsuitable data points}
pop <- subset(full, Include == "Yes")
```
```{r Set variables}
pop$Temp <- as.numeric(pop$Temp)
pop$Real_Temp <- as.numeric(pop$Real_Temp)
pop$Treat <- as.factor(pop$Treat)
pop$Pulse <- as.factor(pop$Pulse)
pop$Bucket <- as.character(pop$Bucket)
pop$Week <- as.numeric(pop$Week)
pop$BACIplus <- as.factor(pop$BDJAACI)
pop$BACIplusfull <- as.factor(pop$BDJAACI_Test)
pop$Infection <- as.numeric(pop$Infection)
pop$Spores <- as.numeric(pop$Spores)
pop$Adults <- as.numeric(pop$Adults)
```
```{r Centre average temperature}
# Centering the 'Real_Temp' variable
pop$Temp_Cent <- scale(pop$Real_Temp, center = TRUE, scale = FALSE)
pop$Temp_Cent <- as.numeric(pop$Temp_Cent)
pop$Week_Cent <- scale(pop$Week, center = TRUE, scale = FALSE)
pop$Week_Cent <- as.numeric(pop$Week_Cent)
pop$Adults_Cent <- scale(pop$Adults, center = TRUE, scale = FALSE)
pop$Adults_Cent <- as.numeric(pop$Adults_Cent)
pop$Spores_Cent <- scale(pop$Spores, center = TRUE, scale = FALSE)
pop$Spores_Cent <- as.numeric(pop$Spores_Cent)

pop$Spores_Scaled <- scale(pop$Spores)
pop$A_Temp <- as.factor(pop$Temp)
```
```{r Specifying order of factors}
pop$BACIplus <- factor(pop$BACIplus, levels = c("C","B","D","JA","A"))
pop$BACIplusfull <- factor(pop$BACIplusfull, levels = c("CB","CD","CJA","CA","PB","PD","PJA","PA"))
```
```{r Adding standard errors for overall trends}
pop <- pop %>%
  group_by(Temp, Treat, Week) %>% 
  mutate(
    # Calculations for Spores overall
    mean.BO = mean(Spores, na.rm = TRUE),
    sd.BO = sd(Spores, na.rm = TRUE),
    se.BO = sd.BO / sqrt(sum(!is.na(Spores))),  # Use sum(!is.na()) to count non-NA values
    
    # Calculations for Adults overall
    mean.AO = mean(Adults, na.rm = TRUE),
    sd.AO = sd(Adults, na.rm = TRUE),
    se.AO = sd.AO / sqrt(sum(!is.na(Adults)))  # Use sum(!is.na()) to count non-NA values
  ) %>%
  ungroup()
```
```{r Subset by temperature for graphing}
fourteen <- subset(pop, Temp == "14") 
seventeen <- subset(pop, Temp == "17")
twenty <- subset(pop, Temp == "20")
twentythree <-subset(pop, Temp == "23")
```

###Burden Model

```{r Weekly Birden}
burden.week <- glmmTMB(Spores ~ poly(Temp, 2) * Treat + Adults + poly(Week_Cent,2) + (1|Bucket), 
                 data = pop, 
                 family = nbinom2)

summary(burden.week)

# Perform Type II (default) or Type III ANOVA
Anova(burden.week, type = "II")  
```

```{r BACI+ Burden}
burden.BACIplus <- glmmTMB(Spores ~ poly(Temp_Cent, 2) * BACIplus + poly(Temp_Cent, 2) * Adults_Cent + (1|Bucket), 
                 data = pop, 
                 family = nbinom12 )

summary(burden.BACIplus)

# Perform Type II (default) or Type III ANOVA
Anova(burden.BACIplus, type = "III")
```

```{r Multicolonearity check}
# Check multicollinearity in the glmmTMB model
check_collinearity(burden.BACIplus)
check_collinearity(burden.week)
```

###Temperature Specific Burden Models 

```{r Fourteen BACI+}
fourteen.BACIplus <- glmmTMB(Spores ~ BACIplus + Adults_Cent + (1|Bucket), 
                 data = fourteen, 
                 family = nbinom2 )

summary(fourteen.BACIplus)

# Perform Type II (default) or Type III ANOVA
Anova(fourteen.BACIplus, type = "III")
```
```{r Seventeen BACI+}
seventeen.BACIplus <- glmmTMB(Spores ~ BACIplus + Adults_Cent + (1|Bucket), 
                 data = seventeen, 
                 family = nbinom2 )

summary(seventeen.BACIplus)

# Perform Type II (default) or Type III ANOVA
Anova(seventeen.BACIplus, type = "III")

####high variance at 17 between buckets might be why it shows weird figures
```
```{r Twenty BACI+}
twenty.BACIplus <- glmmTMB(Spores ~ BACIplus + Adults_Cent + (1|Bucket), 
                 data = twenty, 
                 family = nbinom2 )

summary(twenty.BACIplus)

# Perform Type II (default) or Type III ANOVA
Anova(twenty.BACIplus, type = "III")
```
```{r Twenty Three BACI+}
twentythree.BACIplus <- glmmTMB(Spores ~ BACIplus + Adults_Cent + (1|Bucket), 
                 data = twentythree, 
                 family = nbinom2 )

summary(twentythree.BACIplus)

# Perform Type II (default) or Type III ANOVA
Anova(twentythree.BACIplus, type = "III")
```

###Burden Custom Contrasts

```{r BACIplus emmeans}
#Model used 
BACIplus.burden.posthoc <- glm.nb(Spores ~ A_Temp * BACIplusfull, data = pop)

BACIplus.burden.emm <- emmeans(BACIplus.burden.posthoc, ~ A_Temp * BACIplusfull, data = pop)
BACIplus.burden.emm
```
```{r BACIplus matrix}
  "CB14" = c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CB17" = c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CB20" = c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CB23" = c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD14" = c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD17" = c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD20" = c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD23" = c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA14" = c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA17" = c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA20" = c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA23" = c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA14" = c(0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0)
  "PD14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0)
  "PD17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0)
  "PD20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0)
  "PD23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0)
  "PJA14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0)
  "PJA17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0)
  "PJA20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0)
  "PJA23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0)
  "PA14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0)
  "PA17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0)
  "PA20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0)
  "PA23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)
```
```{r BACIplus custom contrast}
contrast( 
  BACIplus.burden.emm, adjust = "BH", method = list(
  "14CB VS 14PB" = CB14 - PB14,
  "14CD VS 14PD" = CD14 - PD14,
  "14CJA VS 14PJA" = CJA14 - PJA14,
  "14CA VS 14PA" = CA14 - PA14,
  "14PB VS 14PD" = PB14 - PD14,
  "14PB VS 14PJA" = PB14 - PJA14,
  "14PB VS 14PA" = PB14 - PA14,
  
  "17CB VS 17PB" = CB17 - PB17,
  "17CD VS 17PD" = CD17 - PD17,
  "17CJA VS 17PJA" = CJA17 - PJA17,
  "17CA VS 17PA" = CA17 - PA17,
  "17PB VS 17PD" = PB17 - PD17,
  "17PB VS 17PJA" = PB17 - PJA17,
  "17PB VS 17PA" = PB17 - PA17,
  
  "20CB VS 20PB" = CB20 - PB20,
  "20CD VS 20PD" = CD20 - PD20,
  "20CJA VS 20PJA" = CJA20 - PJA20,
  "20CA VS 20PA" = CA20 - PA20,
  "20PB VS 20PD" = PB20 - PD20,
  "20PB VS 20PJA" = PB20 - PJA20,
  "20PB VS 20PA" = PB20 - PA20,
  
  "23CB VS 23PB" = CB23 - PB23,
  "23CD VS 23PD" = CD23 - PD23,
  "23CJA VS 23PJA" = CJA23 - PJA23,
  "23CA VS 23PA" = CA23 - PA23,
  "23PB VS 23PD" = PB23 - PD23,
  "23PB VS 23PJA" = PB23 - PJA23,
  "23PB VS 23PA" = PB23 - PA23))
```

###Graphing Burden

  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.text = element_text(size = 18)) +
  guides(shape = guide_legend(override.aes = list(size = 3))) # Adjust legend appearance

```{r fourteen burden}
fourteen.burden <- ggplot(fourteen, aes(x = Week, y = Spores, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFF1E6", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#FFE2CC", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#FFD4B3", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.BO - se.BO, ymax = mean.BO + se.BO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,24)) +  
  scale_colour_manual(values = c("#999999", "#D55E00")) +
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 800))

fourteen.burden


ggsave("fourteen.burden.png", width = 8, height = 6)
```
```{r seventeen burden}
seventeen.burden <- ggplot(seventeen, aes(x = Week, y = Spores, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFF1E6", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#FFE2CC", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#FFD4B3", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.BO - se.BO, ymax = mean.BO + se.BO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21, 24), labels = c("constant", "heatwave")) +  
  scale_colour_manual(values = c("#999999", "#D55E00"), labels = c("constant", "heatwave")) +
  scale_fill_manual(values = c("#999999", "#D55E00"), labels = c("constant", "heatwave")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks = seq(1, 9, 1)) +
  coord_cartesian(ylim = c(0, 800)) 

seventeen.burden

ggsave("seventeen.burden.png", width = 8, height = 6)
```
```{r twenty burden}
twenty.burden <- ggplot(twenty, aes(x = Week, y = Spores, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E6F6FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#CCECFF", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#B3E3FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.BO - se.BO, ymax = mean.BO + se.BO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill = NA, size = 1)) +
  scale_shape_manual(values = c(21, 25)) +  
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_x_continuous(breaks = seq(1, 9, 1)) +
  coord_cartesian(ylim = c(0, 800))

twenty.burden

ggsave("twenty.burden.png", width = 8, height = 6)
```
```{r twenty three burden}
twentythree.burden <- ggplot(twentythree, aes(x = Week, y = Spores, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E6F6FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#CCECFF", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#B3E3FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.BO - se.BO, ymax = mean.BO + se.BO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,25)) +  
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 800))

twentythree.burden

ggsave("twentythree.burden.png", width = 8, height = 6)
```

###Graphing Population vs Burden

```{r subsetting for means by treatment}

fourteen.week.combo <- fourteen %>%
  group_by(Week) %>%
  summarise(Avg_Adults = mean(Adults, na.rm = TRUE),
            Mean_Spores = mean(Spores, na.rm = TRUE),
            SE_Spores = sd(Spores, na.rm = TRUE) / sqrt(n()),
            SE_Adults = sd(Adults, na.rm = TRUE) / sqrt(n()),# standard error
            .groups = "drop")

seventeen.week.combo <- seventeen %>%
  group_by(Week) %>%
  summarise(Avg_Adults = mean(Adults, na.rm = TRUE),
            Mean_Spores = mean(Spores, na.rm = TRUE),
            SE_Spores = sd(Spores, na.rm = TRUE) / sqrt(n()),
            SE_Adults = sd(Adults, na.rm = TRUE) / sqrt(n()),# standard error
            .groups = "drop")

twenty.week.combo <- twenty %>%
  group_by(Week) %>%
  summarise(Avg_Adults = mean(Adults, na.rm = TRUE),
            Mean_Spores = mean(Spores, na.rm = TRUE),
            SE_Spores = sd(Spores, na.rm = TRUE) / sqrt(n()),
            SE_Adults = sd(Adults, na.rm = TRUE) / sqrt(n()),# standard error
            .groups = "drop")

# Aggregate to mean adults per day-treatment
twentythree.week.combo <- twentythree %>%
  group_by(Week) %>%
  summarise(Avg_Adults = mean(Adults, na.rm = TRUE),
            Mean_Spores = mean(Spores, na.rm = TRUE),
            SE_Spores = sd(Spores, na.rm = TRUE) / sqrt(n()),
            SE_Adults = sd(Adults, na.rm = TRUE) / sqrt(n()),# standard error
            .groups = "drop")

```

```{r fourteen population vs burden combined}
fourteen.pvb.combo <- ggplot(fourteen.week.combo, aes(x = Avg_Adults, y = Mean_Spores)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = Mean_Spores - SE_Spores, ymax = Mean_Spores + SE_Spores), 
                width = 0.2, linewidth = 0.6, position = position_dodge(width = 0.4)) +
  geom_smooth(method = "glm", formula = y ~ poly(x, 2, raw = TRUE), 
              se = FALSE, linetype = "dashed", linewidth = 0.75) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,24)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  coord_cartesian(xlim = c(300,600), ylim = c(0,800))

fourteen.pvb.combo

ggsave("fourteen.pvb.combo.png", width = 8, height = 6)
```
```{r seventeen population vs burden combined}
seventeen.pvb.combo <- ggplot(seventeen.week.combo, aes(x = Avg_Adults, y = Mean_Spores)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = Mean_Spores - SE_Spores, ymax = Mean_Spores + SE_Spores), 
                width = 0.2, linewidth = 0.6, position = position_dodge(width = 0.4)) +
  geom_smooth(method = "glm", formula = y ~ poly(x, 2, raw = TRUE), 
              se = FALSE, linetype = "dashed", linewidth = 0.75) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,24)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  coord_cartesian(xlim = c(300,600), ylim = c(0,800))

seventeen.pvb.combo

ggsave("seventeen.pvb.combo.png", width = 8, height = 6)
```
```{r twenty population vs burden combined}
twenty.pvb.combo <- ggplot(twenty.week.combo, aes(x = Avg_Adults, y = Mean_Spores)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = Mean_Spores - SE_Spores, ymax = Mean_Spores + SE_Spores), 
                width = 0.2, linewidth = 0.6, position = position_dodge(width = 0.4)) +
  geom_smooth(method = "glm", formula = y ~ poly(x, 2, raw = TRUE), 
              se = FALSE, linetype = "dashed", linewidth = 0.75) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,24)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  coord_cartesian(xlim = c(300,600), ylim = c(0,800))

twenty.pvb.combo

ggsave("twenty.pvb.combo.png", width = 8, height = 6)
```
```{r twenty three population vs burden combined}
twentythree.pvb.combo <- ggplot(twentythree.week.combo, aes(x = Avg_Adults, y = Mean_Spores)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = Mean_Spores - SE_Spores, ymax = Mean_Spores + SE_Spores), 
                width = 0.2, linewidth = 0.6, position = position_dodge(width = 0.4)) +
  geom_smooth(method = "glm", formula = y ~ poly(x, 2, raw = TRUE), 
              se = FALSE, linetype = "dashed", linewidth = 0.75) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,24)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  coord_cartesian(xlim = c(300,600), ylim = c(0,800))

twentythree.pvb.combo

ggsave("twentythree.pvb.combo.png", width = 8, height = 6)
```

###Population Model

```{r BACI+ Population}
population.BACIplus <- glmmTMB(Adults ~ poly(Temp_Cent, 3) * BACIplus + poly(Temp_Cent, 3) * Spores_Cent + (1|Bucket), 
                 data = pop, 
                 family = nbinom2)

summary(population.BACIplus)

# Perform Type II (default) or Type III ANOVA
Anova(population.BACIplus, type = "III")  
```

```{r Multicolonearity check}
# Check multicollinearity in the glmmTMB model
check_collinearity(population.BACIplus)
```

###Population Custom Contrasts

```{r BACIplus emmeans}
#Model used 
BACIplus.pop.posthoc <- glm.nb(Adults ~ A_Temp * BACIplusfull, data = pop)

BACIplus.pop.emm <- emmeans(BACIplus.pop.posthoc, ~ A_Temp * BACIplusfull, data = pop)
BACIplus.pop.emm
```
```{r BACIplus matrix}
  "CB14" = c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CB17" = c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CB20" = c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CB23" = c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD14" = c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD17" = c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD20" = c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CD23" = c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA14" = c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA17" = c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA20" = c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CJA23" = c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA14" = c(0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CA23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "PB23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0)
  "PD14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0)
  "PD17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0)
  "PD20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0)
  "PD23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0)
  "PJA14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0)
  "PJA17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0)
  "PJA20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0)
  "PJA23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0)
  "PA14" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0)
  "PA17" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0)
  "PA20" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0)
  "PA23" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)
```
```{r BACIplus custom contrast}
contrast( 
  BACIplus.pop.emm, adjust = "BH", method = list(
  "14CB VS 14PB" = CB14 - PB14,
  "14CD VS 14PD" = CD14 - PD14,
  "14CJA VS 14PJA" = CJA14 - PJA14,
  "14CA VS 14PA" = CA14 - PA14,
  "14PB VS 14PD" = PB14 - PD14,
  "14PB VS 14PJA" = PB14 - PJA14,
  "14PB VS 14PA" = PB14 - PA14,
  
  "17CB VS 17PB" = CB17 - PB17,
  "17CD VS 17PD" = CD17 - PD17,
  "17CJA VS 17PJA" = CJA17 - PJA17,
  "17CA VS 17PA" = CA17 - PA17,
  "17PB VS 17PD" = PB17 - PD17,
  "17PB VS 17PJA" = PB17 - PJA17,
  "17PB VS 17PA" = PB17 - PA17,
  
  "20CB VS 20PB" = CB20 - PB20,
  "20CD VS 20PD" = CD20 - PD20,
  "20CJA VS 20PJA" = CJA20 - PJA20,
  "20CA VS 20PA" = CA20 - PA20,
  "20PB VS 20PD" = PB20 - PD20,
  "20PB VS 20PJA" = PB20 - PJA20,
  "20PB VS 20PA" = PB20 - PA20,
  
  "23CB VS 23PB" = CB23 - PB23,
  "23CD VS 23PD" = CD23 - PD23,
  "23CJA VS 23PJA" = CJA23 - PJA23,
  "23CA VS 23PA" = CA23 - PA23,
  "23PB VS 23PD" = PB23 - PD23,
  "23PB VS 23PJA" = PB23 - PJA23,
  "23PB VS 23PA" = PB23 - PA23))
```

###Graphing Population

```{r fourteen population}
fourteen.population <- ggplot(fourteen, aes(x = Week, y = Adults, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFF1E6", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#FFE2CC", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#FFD4B3", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Adults, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 3), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.AO - se.AO, ymax = mean.AO + se.AO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,24)) +  
  scale_colour_manual(values = c("#999999", "#D55E00")) +
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 800))

fourteen.population

ggsave("fourteen.population.png", width = 8, height = 6)
```
```{r seventeen population}
seventeen.population <- ggplot(seventeen, aes(x = Week, y = Adults, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFF1E6", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#FFE2CC", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#FFD4B3", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Adults, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 3), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.AO - se.AO, ymax = mean.AO + se.AO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21, 24), labels = c("constant", "heatwave")) +  
  scale_colour_manual(values = c("#999999", "#D55E00"), labels = c("constant", "heatwave")) +
  scale_fill_manual(values = c("#999999", "#D55E00"), labels = c("constant", "heatwave")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks = seq(1, 9, 1)) +
  coord_cartesian(ylim = c(0, 800)) 

seventeen.population

ggsave("seventeen.population.png", width = 8, height = 6)
```
```{r twenty population}
twenty.population <- ggplot(twenty, aes(x = Week, y = Adults, colour = Treat, shape = Treat, fill = Treat)) +
  # Add shaded region from Week 5 onward
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E6F6FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#CCECFF", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#B3E3FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Adults, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 3), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.AO - se.AO, ymax = mean.AO + se.AO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill = NA, size = 1)) +
  scale_shape_manual(values = c(21, 25)) +  
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_x_continuous(breaks = seq(1, 9, 1)) +
  coord_cartesian(ylim = c(0, 800))

twenty.population

ggsave("twenty.population.png", width = 8, height = 6)
```
```{r twenty three population}
twentythree.population <- ggplot(twentythree, aes(x = Week, y = Adults, colour = Treat, shape = Treat, fill = Treat)) +
  geom_rect(aes(xmin = 5.5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E6F6FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 5.5, xmax = 6.5, ymin = -Inf, ymax = Inf),
            fill = "#CCECFF", alpha = 0.2, inherit.aes = FALSE) +
  geom_rect(aes(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf),
            fill = "#B3E3FF", alpha = 0.4, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Adults, colour = Treat),
              method = "glm.nb", formula = y ~ poly(x, 3), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean.AO - se.AO, ymax = mean.AO + se.AO), 
                width = 0.2, position = position_dodge(width = 0.4)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_shape_manual(values = c(21,25)) +  
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 800))

twentythree.population

ggsave("twentythree.population.png", width = 8, height = 6)
```

###Compare to Individual Experiments

```{r Import data eet}
compare <- read.csv("Exp_comp.csv", header = TRUE, stringsAsFactors = FALSE)
```
```{r Set variables}
compare$Exp <- as.character(compare$Exp)
compare$Period <- as.factor(compare$Period)
compare$A_Temp <- as.factor(compare$A_Temp)
compare$Real_Avg <- as.numeric(compare$Real_Avg)
compare$Treat <- as.factor(compare$Treat)
compare$Spores <- as.numeric(compare$Spores)
compare$Exposed <- as.numeric(compare$Exposed)
```
```{r Centre average temperature}
# Centering the 'Real_Avg' variable
compare$Real_Avg_Cent <- scale(compare$Real_Avg, center = TRUE, scale = FALSE)
compare$Real_Avg_Cent <- as.numeric(compare$Real_Avg_Cent)
```
```{r Specifying order of factors}
compare$Period <- factor(compare$Period, levels = c("C","D","JA","A"))
```
```{r Adding Standard Errors for Overall trends}
compare <- compare %>%
  group_by(Exp, A_Temp, Treat, Period) %>% 
  mutate(
    # Calculations for Burden overall
    mean.BO = mean(Spores, na.rm = TRUE),
    sd.BO = sd(Spores, na.rm = TRUE),
    se.BO = sd.BO / sqrt(sum(!is.na(Spores))),  # Use sum(!is.na()) to count non-NA values

    # Calculations for Exposure overall
    mean.EO = mean(Exposed, na.rm = TRUE),
    sd.EO = sd(Exposed, na.rm = TRUE),
    se.EO = sd.EO / sqrt(sum(!is.na(Exposed)))  # Use sum(!is.na()) to count non-NA values
  ) %>%
  ungroup()
```

```{r Subset by temperature for graphing during only}
fourteen.pop.dur <- subset(compare, A_Temp == "14" & Exp == "POP" & Period %in% c("C","D")) 
fourteen.ind.dur <- subset(compare, A_Temp == "14" & Exp == "HW" & Period %in% c("C","D")) 
seventeen.pop.dur <- subset(compare, A_Temp == "17" & Exp == "POP" & Period %in% c("C","D")) 
seventeen.ind.dur <- subset(compare, A_Temp == "17" & Exp == "HW" & Period %in% c("C","D")) 
twenty.pop.dur <- subset(compare, A_Temp == "20" & Exp == "POP" & Period %in% c("C","D")) 
twenty.ind.dur <- subset(compare, A_Temp == "20" & Exp == "CS" & Period %in% c("C","D")) 
twentythree.pop.dur <-subset(compare, A_Temp == "23" & Exp == "POP" & Period %in% c("C","D")) 
twentythree.ind.dur <-subset(compare, A_Temp == "23" & Exp == "CS" & Period %in% c("C","D")) 
```

```{r For making legends}
fourteen.pop.legend <- ggplot(fourteen.pop.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax = mean.EO + se.EO, colour = Period), width = 0.2) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#D55E00"), 
                      name = "Treatment",  # Legend title
                      labels = c("Constant", "Heatwave")) +  # Custom legend labels
  scale_fill_manual(values = c("#999999", "#D55E00"), 
                    name = "Treatment", 
                    labels = c("Constant", "Heatwave")) +  
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), 
        legend.position = "top",  # Move legend above panel
        legend.justification = "center",
        legend.text = element_text(size = 16),  # Bigger legend text
        legend.title = element_text(size = 18)) + # Bigger legend title
  coord_cartesian(ylim = c(0, 1500))

fourteen.pop.legend
```

```{r fourteen population during only}
fourteen.pop.dur.sp <- ggplot(fourteen.pop.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#D55E00")) +
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  coord_cartesian(ylim = c(0, 1500))

fourteen.pop.dur.sp

ggsave("fourteen.pop.dur.sp.png", width = 4, height = 6)
```
```{r fourteen individual during only}
fourteen.ind.dur.sp <- ggplot(fourteen.ind.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#D55E00")) +
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_y_continuous(position = "right") +
  guides(color = "none") +
  coord_cartesian(ylim = c(0, 1500))

fourteen.ind.dur.sp

ggsave("fourteen.pop.ind.sp.png", width = 4, height = 6)
```
```{r seventeen population during only}
seventeen.pop.dur.sp <- ggplot(seventeen.pop.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#D55E00")) +
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  coord_cartesian(ylim = c(0, 1500))

seventeen.pop.dur.sp

ggsave("seventeen.pop.dur.sp.png", width = 4, height = 6)
```
```{r seventeen individual during only}
seventeen.ind.dur.sp <- ggplot(seventeen.ind.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#D55E00")) +
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  coord_cartesian(ylim = c(0, 1500))

seventeen.ind.dur.sp

ggsave("seventeen.ind.dur.sp.png", width = 4, height = 6)
```
```{r twenty population during only}
twenty.pop.dur.sp <- ggplot(twenty.pop.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  coord_cartesian(ylim = c(0, 1500))

twenty.pop.dur.sp

ggsave("twenty.pop.dur.sp.png", width = 4, height = 6)
```
```{r twenty individual during only}
twenty.ind.dur.sp <- ggplot(twenty.ind.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  coord_cartesian(ylim = c(0, 1500))

twenty.ind.dur.sp

ggsave("twenty.ind.dur.sp.png", width = 4, height = 6)
```
```{r twenty three population during only}
twentythree.pop.dur.sp <- ggplot(twentythree.pop.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  coord_cartesian(ylim = c(0, 1500))

twentythree.pop.dur.sp

ggsave("twentythree.pop.dur.sp.png", width = 4, height = 6)
```
```{r twenty three individual during only}
twentythree.ind.dur.sp <- ggplot(twentythree.ind.dur, aes(x = Period, y = Exposed, colour = Period)) +
  stat_summary(fun = "mean", geom = "point", size = 3.5) +
  geom_errorbar(aes(ymin = mean.EO - se.EO, ymax =  mean.EO + se.EO), width = 0.2) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_colour_manual(values = c("#999999", "#0072B2")) +
  scale_fill_manual(values = c("#999999", "#0072B2")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_y_continuous(position = "right") +
  coord_cartesian(ylim = c(0, 1500))

twentythree.ind.dur.sp

ggsave("twentythree.ind.dur.sp.png", width = 4, height = 6)
```

Custom Contrasts:

```{r Make new treatment column}
compare$Treatment <- with(compare, paste(Exp, A_Temp, Treat, Period, sep = "_"))
```

```{r Compare during emmeans}
during <- subset(compare, Period %in% c("C","D")) 

#Model used 
during.posthoc <- glm.nb(Spores ~ Treatment, data = during)

during.emmeans <- emmeans(during.posthoc, ~ Treatment, data = during)
during.emmeans
```
```{r Compare during matrix}
  "CS_20_C_C"   = c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CS_20_CS_D"  = c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CS_23_C_C"   = c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0)
  "CS_23_CS_D"  = c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0)
  "HW_14_C_C"   = c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0)
  "HW_14_HW_D"  = c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0)
  "HW_17_C_C"   = c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0)
  "HW_17_HW_D"  = c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0)
  "POP_14_C_C"  = c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0)
  "POP_14_HW_D" = c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0)
  "POP_17_C_C"  = c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0)
  "POP_17_HW_D" = c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0)
  "POP_20_C_C"  = c(0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0)
  "POP_20_CS_D" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0)
  "POP_23_C_C"  = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0)
  "POP_23_CS_D" = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)
```
```{r Compare during custom contrast}
contrast( 
  during.emmeans, adjust = "BH", method = list(
  "14P.D VS 14P.C"   = POP_14_HW_D - POP_14_C_C,
  "14I.D VS 14I.C"   = HW_14_HW_D - HW_14_C_C,
  "17P.D VS 17P.C"   = POP_17_HW_D - POP_17_C_C,
  "17I.D VS 17I.C"   = HW_17_HW_D - HW_17_C_C,
  "20P.D VS 20P.C"   = POP_20_CS_D - POP_20_C_C,
  "20I.D VS 20I.C"   = CS_20_CS_D - CS_20_C_C,
  "23P.D VS 23P.C"   = POP_23_CS_D - POP_23_C_C,
  "23I.D VS 23I.C"   = CS_23_CS_D - CS_23_C_C))
```
```{r Compare during everything custom contrast}
contrast( 
  during.emmeans, adjust = "BH", method = list(
  "14P.D VS 14P.C"   = POP_14_HW_D - POP_14_C_C,
  "14I.D VS 14I.C"   = HW_14_HW_D - HW_14_C_C,
  "14P.D VS 14I.D"   = POP_14_HW_D - HW_14_HW_D,
  "14P.C VS 14I.C"   = POP_14_C_C - HW_14_C_C,
  
  "17P.D VS 17P.C"   = POP_17_HW_D - POP_17_C_C,
  "17I.D VS 17I.C"   = HW_17_HW_D - HW_17_C_C,
  "17P.D VS 17I.D"   = POP_17_HW_D - HW_17_HW_D,
  "17P.C VS 17I.C"   = POP_17_C_C - HW_17_C_C,
 
  "20P.D VS 20P.C"   = POP_20_CS_D - POP_20_C_C,
  "20I.D VS 20I.C"   = CS_20_CS_D - CS_20_C_C,
  "20P.D VS 20I.D"   = POP_20_CS_D - CS_20_CS_D,
  "20P.C VS 20I.C"   = POP_20_C_C - CS_20_C_C,
 
  "23P.D VS 23P.C"   = POP_23_CS_D - POP_23_C_C,
  "23I.D VS 23I.C"   = CS_23_CS_D - CS_23_C_C,
  "23P.D VS 23I.D"   = POP_23_CS_D - CS_23_CS_D,
  "23P.C VS 23I.C"   = POP_23_C_C - CS_23_C_C))
```

####Graphing Burden Buckets

```{r fourteen constant graph}
fourteen.con <- ggplot(fourteen.c, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFECDD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

fourteen.con

ggsave("fourteen.con.png", width = 8, height = 6)
```

```{r seventeen constant graph}
seventeen.con <- ggplot(seventeen.c, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFECDD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

seventeen.con

ggsave("seventeen.con.png", width = 8, height = 6)
```

```{r twenty constant graph}
twenty.con <- ggplot(twenty.c, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E5F3FD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

twenty.con

ggsave("twenty.con.png", width = 8, height = 6)
```

```{r twentythree constant graph}
twentythree.con <- ggplot(twentythree.c, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E5F3FD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  guides(color = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

twentythree.con

ggsave("twentythree.con.png", width = 8, height = 6)
```

```{r fourteen pulse graph}
fourteen.pulse <- ggplot(fourteen.p, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFECDD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  scale_y_continuous(position = "right") +
  coord_cartesian(ylim = c(0, 1500))

fourteen.pulse

ggsave("fourteen.pulse.png", width = 8, height = 6)
```

```{r seventeen pulse graph}
seventeen.pulse <- ggplot(seventeen.p, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#FFECDD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

seventeen.pulse

ggsave("seventeen.pulse.png", width = 8, height = 6)
```

```{r twenty pulse graph}
twenty.pulse <- ggplot(twenty.p, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E5F3FD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

twenty.pulse

ggsave("twenty.pulse.png", width = 8, height = 6)
```

```{r twentythree pulse graph}
twentythree.pulse <- ggplot(twentythree.p, aes(x = Week, y = Spores, colour = Bucket)) +
  geom_rect(aes(xmin = 5, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#E5F3FD", alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(aes(x = Week, y = Spores, colour = Bucket),
              method = "glm.nb", formula = y ~ poly(x, 2), se = F, linewidth = 0.75, lty = "dashed") +
  stat_summary(fun = "mean", geom = "point", size = 3, position = position_dodge(width = 0.6)) +
  geom_errorbar(aes(ymin = mean.BV - se.BV, ymax = mean.BV + se.BV), 
                width = 0.2, position = position_dodge(width = 0.6)) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.text = element_text(size = 18), legend.position = "none") +
  scale_y_continuous(position = "right") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  coord_cartesian(ylim = c(0, 1500))

twentythree.pulse 

ggsave("twentythree.pulse.png", width = 8, height = 6)
```



















